\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Added Figure 12 title

```{r}
#| label: best-fit-umap-tsne
#| fig-cap: "Best fit"
#| fig-width: 10
#| fig-height: 20

>>>>

```{r}
#| label: best-fit-umap-tsne
#| fig-cap: "Best fit using UMAP ($a_1$ = 0.09) and tSNE ($a_1$ = 0.16) with the same number of non-empty bins ($m$ = 39). Both models show twist in $7\\text{-}D$."
#| fig-width: 10
#| fig-height: 20

### 2024-10-01 paper.tex
Updated Figure 10
Added Figure 12 title

\caption{Wireframes with Delaunay triangulation, and two choices of edge
removal in \gD{} and \pD{}.}

@@

\caption{Best fit}

>>>>

\caption{Distribution of edge lengths and wireframes in \gD{} and
\(7\text{-}D\) with Delaunay triangulation, and two choices of long edge
removal.}

@@

\caption{Best fit using UMAP (\(a_1\) = 0.09) and tSNE (\(a_1\) = 0.16)
with the same number of non-empty bins (\(m\) = 39). Both models show
twist in \(7\text{-}D\).}
